# Data Wrangling

## Load Packages

```{r eval = FALSE}
library(tidyverse)
library(knitr)
library(lubridate)

```


## Load csv


```{r}

rabbits <- read.csv(
  "/Users/tthorpe7/Documents/Vernal_Project/Working_Data/Vernal_All_data_prep_for_R_rabbits.csv")


```


## Check csv imported properly

Even though things look right with head(), the dimensions 998 x 26 are incorrect. In Excel, there are only 49 rows. Why did this happen? It looks like extra rows and columns were created with NA values.

```{r}

head(rabbits)
dim(rabbits)

```


I think the easiest fix will be to subset the data.

```{r}

rabbits <- rabbits[1:49, 1:10]

```


Now we have isolated the data and can begin fixing it. Let's start with the date.

```{r}

rabbits$Date <- lubridate::mdy(rabbits$Date)
class(rabbits$Date)


```
Now the "Date" column values are stored as dates instead of characters. I will do the same for the time columns.

```{r}

rabbits$Start.Time <- lubridate::hm(rabbits$Start.Time)

rabbits$End.Time <- lubridate::hm(rabbits$End.Time)

class(rabbits$Start.Time)

class(rabbits$End.Time)

```
