# Build a figure

## I would like to work toward building a figure showing counts of the various rabbit species over time (dates). I may need to further manipulate the data so it is arranged in a way I can plot it.

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(ggridges)
library(viridis)
library(lubridate)

```

## Pivot the data

```{r}

rab_long <- rabbits %>%
            pivot_longer(cols = c("Cottontail.Count", "Jackrabbit.Count",
                                            "Snowshoe.Hare.Count", "Unknown.Count"), 
                                  names_to = "species", values_to = "count") %>%
            view()

```

## Now we are ready to plot! Hopefully...

```{r}

ggplot(data = rab_long, aes(x = Date, y = count, color = species)) +
  geom_point() +
  geom_line()

```

I made a rough plot of the data, but I don't like how the zeros are plotted this way. I need to explore other options.

## Trying something else.

```{r}

ggplot(data = rab_long, aes(x = Date, y = count, fill = species, height = count)) +
geom_ridgeline()

```

This is really ugly! I have to keep trying.

## Another one

I think I should filter out the 0's in my data since they are implied.

```{r}

rab_long <- rab_long %>%
             filter(count != 0) %>%
             view()

```

This seems to have accomplished what I wanted!

```{r}
ggplot(data = rab_long, aes(x = Date, y = count, color = species, fill = species)) +
  geom_point(shape = 21) +
  ylim(0, 4) +
  theme_bw()


```

I don't think this is the best way to display the data, so I am going to just show species total each month.

```{r}

rab_simple <- rab_long %>%
dplyr::group_by(month(Date), species) %>%
  tally()

rab_simple <- rab_simple %>%
  as.tibble() %>%
  rename("mo" = "month(Date)")

ggplot(data = rab_simple, aes(x = mo, y = n, fill = species)) +
geom_bar(stat = "identity", position = "dodge") +
  theme_bw() +
  scale_x_continuous(breaks = unique(rab_simple$mo), minor_breaks = NULL,
                     labels = c("March", "April")) +
  labs(x = "Month", y = "Count", fill = "Species") +
  ggtitle("2022 Rabbit Detections")  +
  theme(axis.ticks.x = element_blank()) +
  scale_fill_viridis_d(labels = c("Cottontails", "Jackrabbits", "Unknown species"))

```
 
I feel like this is finally pretty good, but I will try to make it even better.

## Final Figure

I am copying and pastying the previous code and adding to it.

```{r}

ggplot(data = rab_simple, aes(x = mo, y = n, fill = species)) +
geom_bar(stat = "identity", position = position_dodge(width = 1)) +
  theme_bw() +
  scale_x_continuous(breaks = unique(rab_simple$mo), minor_breaks = NULL,
                     labels = c("March", "April")) +
  labs(x = "Month", y = "Count", fill = "Species") +
  ggtitle("2022 Rabbit Detections")  +
  theme(plot.title = element_text(hjust = 0.5, size = 20)) +
  theme(axis.title.y = element_text(margin = margin(r = 12))) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.ticks.x = element_blank()) +
  scale_fill_viridis_d(labels = c("Cottontails", "Jackrabbits", "Unknown species"))

```

## The Takeaway

This took a lot of time, but it was great practice. I have learned so much and I am excited to apply my skills to my data. :)



